---
title: "results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
get_columns<-function(colname){
  cols<-lapply(gene_list$V1, function(i){
      f<-read.table(paste0(output_dir, i), header = T)
      return(f[, colname])
  })
  output<-do.call(cbind, cols)
  return(data.frame(f$Category, output))
}
```

```{r}
#count number of reference SNPs in Category C
annotations<-read.table("/project2/xuanyao/jing/reference/baseline/baseline.21.annot.gz", header = T)
counts<-unlist(apply(annotations[, 5:length(names(annotations))], 2, sum))
```

### summarize results across genes
#### Chromosome 21
```{r echo = FALSE}
output_dir<-"/home/jinggu/scratch-midway2/projects/gene_heritability/chr21/output/"
gene_list<-read.table(paste0(output_dir, "all_genes.txt"), header = F)
f<-read.table(paste0(output_dir, "N6AMT1_local_SNPs.results"), header = T)
```
* average per SNP heritability for category Cc across all genes 
```{r}
tau<-get_columns("Coefficient")
avg_tau<-apply(tau[, -1], 1, sum)
hist(avg_tau, main = "Average Tau_C across all genes")
```
* total Heritability estimates
```{r}
total_h2<-sum(counts*avg_tau)
counts*avg_tau
total_h2
```
#### Chromosome 22
```{r echo = FALSE}
output_dir<-"/home/jinggu/scratch-midway2/projects/gene_heritability/chr22/output/"
gene_list<-read.table(paste0(output_dir, "all_genes.txt"), header = F)
f<-read.table(paste0(output_dir, "ZNF280B_local_SNPs.results"), header = T)
```

```{r}
#count number of reference SNPs in Category C
annotations<-read.table("/project2/xuanyao/jing/reference/baseline/baseline.22.annot.gz", header = T)
counts<-unlist(apply(annotations[, 5:length(names(annotations))], 2, sum))
```
* average per SNP heritability for category Cc across all genes 
```{r}
tau<-get_columns("Coefficient")
avg_tau<-apply(tau[, -1], 1, sum)
hist(avg_tau, main = "Average Tau_C across all genes")
```
* total Heritability estimates
```{r}
total_h2<-sum(counts*avg_tau)
counts*avg_tau
total_h2
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
